Combining information from photometric and spectroscopic data:\\ propogating uncertainties in spectrophotometric calibration

### 2015-05-11 tex/figures.tex
fix bugs in uncertainties plotting for dashboards and in setting the speccal directory in paramfiles, add text about photometry beyond the spectra even with perfect spec cal
param file and plotting code for real data

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/ideal.pdf}
\caption{Results of inference from a mock spectrum and a single photometric data point where the spectrophotometric calibration is assumed to be perfectly known.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: The calibration vector. In this case the true calibration
vector ({\it black}) is a constant and it is not inferred as part of
the model
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_ideal}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from a \emph{perfectly calibrated} mock
  spectrum and a single photometric data point, where uncertainties in
  the calibration are modeled.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it green}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.  Panels and colors are
  as in Figure \ref{fig:speconly_calibrated}.  In this case the
  observed spectrum is in arbitrary units and the true
  calibration vector is not a constant with wavelength.
\label{fig:speconly_uncalibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Results of inference from the combination of
  \emph{uncalibrated} spectroscopy and all the photometric data
  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
\label{fig:specphot_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Joint posterior PDFs for several physical parameters. The
  posteriors obtained from photometry only is in {\it red}, from
  \emph{uncalibrated} spectroscopy and a single photometric point in {\it blue}, and from
  the photometry and spectroscopy combined in {\it magenta}.
\label{fig:combined_posterior}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Posterior PDFs obtained from mock spectra and photometry
  created with  a variety of mock physical parameters, as a function
  of those parameters.
\label{fig:mock_parameter_space}}
\end{figure*}

>>>>

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/ideal.pdf}
\caption{Results of inference from a mock spectrum and a single
  photometric data point where the spectrophotometric calibration is
  assumed to be perfectly known. 
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters.
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical black lines.
{\color{red} Remove calibration plot and intrinsic plot, since it is
  the same as observed spectrum.  Show residuals.}
\label{fig:speconly_ideal}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_calibrated.pdf}
\caption{Results of inference from a \emph{perfectly calibrated} mock
  spectrum and a single photometric data point, where uncertainties in
  the calibration are modeled.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it green}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
 {\color{red} This is not converged.  mass and dust2 PDFs will become
   much broader.}
\label{fig:speconly_calibrated}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_uncalibrated.pdf}
\caption{Results of inference from an \emph{uncalibrated} mock
  spectrum and a single photometric data point.  Panels and colors are
  as in Figure \ref{fig:speconly_calibrated}.  In this case the
  observed spectrum is in arbitrary units and the true
  calibration vector is not a constant with wavelength.
 {\color{red} This is not converged.}
\label{fig:speconly_uncalibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
\caption{Results of inference from the combination of
  \emph{uncalibrated} spectroscopy and all the photometric data
  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
\label{fig:specphot_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/combined_post.pdf}
\caption{Joint posterior PDFs for several physical parameters. The
posteriors obtained from photometry only are in {\it red}, from
\emph{uncalibrated} spectroscopy and a single photometric point in
{\it blue}, and from the photometry and spectroscopy combined in {\it
magenta}.  The contours are 1 and 2-sigma contours. The true values
are indicated by {\it black points}.
\label{fig:combined_posterior}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset from the input parameters of the medians of the
posterior PDFs for model parameters obtained from mock spectra and
photometry. Lines connect a single model.
 \label{fig:mock_parameter_space}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{The value of more photometry. Marginalized posterior PDFs
obtained from mock spectra and photometry, for different numbers of
photometric bands.  The pdfs $g$-band only ({\it red}), $g$- and $i-$
band ({\it blue}), and the combined SDSS $griz$ and 2MASS $JHK_s$ set of
bands ({\it orange}).
\label{fig:vary_phot}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inference from a real, calibrated, spectrum.  Top left:
  Observed spectrum and posterior samples thereof.  Bottom left:
  residuals.  Top right: inferred calibration vector, samples.
  Bottom right: posterior PDFs (corner plot?) for physical parameters.
\label{fig:real_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inference from a real, uncalibrated, spectrum.  Top left:
  Observed spectrum and posterior samples thereof.  Bottom left:
  residuals.  Top right: inferred calibration vector, samples.
  Bottom right: posterior PDFs (corner plot?) for physical parameters.
\label{fig:real_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Ratio of the calibration vector inferred from the
  real uncalibrated spectrum to that inferred from the real calibrated
  spectrum ({\it green}). Taking the ratio reduces the effects of model
  imperfections and shows how well we are able to infer the
  calibration vector of \citet{schiavon05} ({\it black}).  
\label{fig:real_calibration_ratio}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inferred parameters for \excluster.  We show the inference from the
  calibrated spectrum ({\it red}), from the uncalibrated spectrum
  ({\it blue}), and from the CMD ({\it black}).
\label{fig:real_parameters}}
\end{figure*}

### 2015-05-11 tex/ms.tex
param file and plotting code for real data

We take the calibration-vector that modifies the mean model to produce
the observed spectrum as multiplicative with respect to the mean
model.  In this case we define the residual of the data from the model
in terms of the logarithmic differences.  This logarithmic formulation
requires that $d$ be everywhere positive, and distorts the
uncertainties, especially at low S/N ratio.  The advantages of
defining the residual in this way are that the model remains linear
(and therefore fast) and the calibration vector is forced to be
positive everywhere.  Additionally, at high signal to noise the
distortion of the uncertainties will be minimal.

{\color{blue} BDJ This paragraph should explain why we are using the
GP, not just how it works.}
The multiplicative calibration vector can be explicitly modeled, for
example using polynomials.  However, for complex calibration vectors
over large wavelength ranges, the number of parameters required to
model the calibration can become quite large (e.g., very high order
polynomials) and the correct parameterization may be unknown.  It is
therefore desirable to introduce a non-parameteric model of the
calibration.  We do this using a Gaussian Process: prior over
functions, analytically marginalizable, covariant fractional
uncertainties the same as multiplying by a function (covariant
uncertainties the same as adding a function)

@@

We are now left to demonstrate that, by including photometry as well
as spectroscopy, it is possible to infer the parameters of interest
$\theta$ while marginalizing over the calibration parameters $\alpha$.
We will apply the methodology for spectrophotometric calibration
described above to both \emph{mock} and \emph{real} optical spectra of
Galactic globular clusters.  Spectra of globular clusters provide a
good test case, as they are less complex than galaxy spectra (for
which it is necessary to model the star formation history) but are by
no means trivial. In this way the key features of the calibration
model and methodology are not obscured.  Additionally, information
about the physical parameters of the cluster is available from
resolved stellar CMDs, providing an important check on our inference
methodology and especially our population synthesis models.

@@

The data we use to test our method consist of optical spectroscopy of
of galactic globular clusters from \citet{schiavon05} for which
optical and NIR photometry are available. The optical spectra were
obtained by drift-scanning a long-slit spectrograph across the
cluster.  The wavelength range of the spectra is $3500-6500$\AA. The
instrumental resolution is $\sim 3.1$\AA~ at $\sim 4500\AA$ and varies
with wavelength.  These spectra have been placed on the rest-frame,
though in what follows we will model the effect of redshift
uncertainties on the data.

An example spectrum (and the inferred spectrophotometric calibration
vector) is shown in Figure \ref{fig:ggc_data}.  As stated by
\citet{schiavon05}, the spectrophotometric calibration of these data
are only approximate.  When fitting the spectra we mask the region
around the bright OI5577\AA~ sky line, and we fit only to the spectrum
with $3550\AA < \lambda < 6500$\AA~ which are covered by the MILES
spectral library (see \S\ref{sec:cluster_model}).  Absorption lines of
the interstellar medium (ISM) can significantly affect the spectrum,
so we additionally mask the Calcium H and K lines and the NaD doublet.

Words about photometry.

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray} \label{eq:StarModel}\displaystyle
f_{\theta_s}(\lambda_o) & = &
L(\sigma_s, z) ,\, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
The matrix $L(\sigma_s, z)$ is a convolution kernel representing the
stellar velocity profile,
and $\sigma_s$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

The model spectra $f_{\theta_s}$ are smoothed by convolution with
the line-spread function of the spectrograph and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift. For computational simplicity we assume that
the internal velocity dispersion of the cluster is negligible compared
to the instrumental broadening, though in principle it can and should
also be modeled. The instrumental resolution is given by the parameter
$\sigma_{inst}$.  {\color{blue}Discuss intrinsic resolution of model spectra
(MILES), what to do in situations where instrumental resolution is
higher, lower or comparable (ouch) to intrinsic velocity broadening.}

@@

\item Real calibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model. The calibration vector
  inferred will highlight differences between the calibrated spectrum
  and the model (which could either be due to calibration problems or
  model problems)

\item Real uncalibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model. This is to show how much
  the inferred physical parameters change when the calibration is
  basically unknown.

@@

For each test we want to show
\begin{itemize}

\item Posterior parameter pdfs (and joint pdfs).

\item Samples of the posterior prediction for the observations, and
  residuals thereform.

\item The calibration vector, and posterior samples of it.

\item Posterior samples of the intrinsic spectrum
\end{itemize}

@@

{\color{blue}BDJ Describe results from the ideal case.}

Next we will \emph{not} assume that the calibration is perfectly known
and we will therefore allow the calibration parameters $\alpha$ in our
model to vary.  In Figure
\ref{fig:speconly_calibrated} we show the result of our inference from
the spectrum and a single photometric measurement (SDSS $g$) for a
perfectly calibrated mock spectrum. To demonstrate the quality of the
fit we show both the mock input spectrum and predictions of the
observed spectra that result from several draws of the model
parameters $[\theta, \alpha]$ from posterior distribution.  We also
show samples of the inferred calibration vector,
\begin{eqnarray} \label{eq:calibration}
\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
\quad ,
\end{eqnarray}
where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
logarithmic residual between the data and the model \citep{RW}.  For the
perfectly calibrated spectrum the true calibration vector (shown in
black) is one everywhere.  The spread of the inferred calibration
vectors approximately indicates our uncertainty in the spectrophotometric
calibration when no additional calibration information is available
and only a single photometric point is available.

Even in the case of a single photometric data point, many of the
physical parameters are well-constrained and only minimally biased,
e.g. age and metallicity.  These are the parameters that are
constrained well by the spectrum itself and are not strongly sensitive
to the overall shape of the spectral continuum.  Such parameters can
be reasonably well recovered by fitting continuum normalized spectra,
though here we have propogated the uncertainty in this normalization
into the uncertainties on the physical parameters.

On the other hand, the posterior PDF for the dust attenuation optical
depth $A_v$ is extremely broad.

The uncertainty on the total stellar mass incorporates both the
uncertainty in the photometric flux and the uncertainty in the $g$-
band mass-to-light ratio.

In Figure \ref{fig:speconly_uncalibrated} we show the results of
inference on an \emph{uncalibrated} mock spectrum.

>>>>

For the spectroscopic measurements we are going to account for
the spectrophotometric calibration in our likelihood function.  We
take this calibration-vector that modifies the mean spectroscopic
model to produce the observed spectrum to be multiplicative with
respect to the mean model.  In this case we define the residual of the
data from the model in terms of the logarithmic differences.  This
logarithmic formulation requires that $d$ be everywhere positive, and
distorts the uncertainties, especially at low S/N ratio.  The
advantages of defining the residual in this way are that the model
remains linear (and therefore fast) and the calibration vector is
forced to be positive everywhere.  Additionally, at high signal to
noise the distortion of the uncertainties will be minimal.

{\color{blue} BDJ This paragraph should explain why we are using the
GP, not just how it works.}
The multiplicative calibration vector can be explicitly modeled, for
example using polynomials.  However, for complex calibration vectors
over large wavelength ranges, the number of parameters required to
model the calibration can become quite large (e.g. very high order
polynomials) and the correct parameterization may be unknown.  It is
therefore desirable to introduce a non-parameteric model of the
calibration.  We do this using a Gaussian Process: BDJ: prior over
functions, analytically marginalizable, covariant fractional
uncertainties the same as multiplying by a function (covariant
uncertainties the same as adding a function)

@@

We are now left to demonstrate that, by including photometry as well
as spectroscopy, it is possible to infer the parameters of interest
$\theta$ while marginalizing over the calibration parameters $\alpha$.
We will apply the methodology for spectrophotometric calibration
described above to both \emph{mock} and \emph{real} optical spectra of
Galactic globular clusters.  Spectra of globular clusters provide a
good test case, as they are less complex than galaxy spectra (for
which it is necessary to model the star formation history) but are by
no means trivial. In this way the key features of the calibration
model and methodology are not obscured.  Additionally, information
about the physical parameters of the cluster is available from
resolved stellar CMDs, providing an important check on our inference
methodology and especially our models for star cluster spectra.  However,
our methodology is applicable any spectral model: stars, galaxies or
ISM emission.

@@

The data we use to test our method consist of optical spectroscopy of
of galactic globular clusters from \citet{schiavon05} for which
optical and NIR photometry are available. The optical spectra were
obtained by drift-scanning a long-slit spectrograph across the
cluster.  The wavelength range of the spectra is $3500-6500$\AA. The
instrumental resolution is $\sim 3.1$\AA~ at $\sim 4500\AA$ and varies
with wavelength.  These spectra have been placed on the rest-frame,
though in throughout our analysis we allow the redshift to vary as one
of the model parameters.

An example spectrum (and the inferred spectrophotometric calibration
vector) is shown in Figure \ref{fig:ggc_data}.  As stated by
\citet{schiavon05}, the spectrophotometric calibration of these data
are only approximate.  When fitting the spectra we mask the region
around  several bright sky lines, and we fit only to the spectrum
with $3550\AA < \lambda < 6500$\AA~ which are covered by the MILES
spectral library (see \S\ref{sec:cluster_model}).  Absorption lines of
the interstellar medium (ISM) can significantly affect the spectrum,
so we additionally mask the Calcium H and K lines and the NaD doublet.

The line-spread function of the data is not constant as a function of
velocity or wavelength.  While a wavelength dependent line spread
function can be included in the model, it is computationally
intensive. Therefore, we have convolved the observed spectra with a
wavelength-dependent kernel to bring it to an approximately constant
dispersion in wavelength across the whole spectrum. This dispersion is
a free parameter in our model.

Optical photometry is available from \citep{vanderbeke14} based on
SDSS for objects in the northern hemisphere and on data from CTIO for
southern hemisphere objects.  Briefly, total fluxes within the half-light radii
of the clusters \citet{harris98} were calculated, with small
corrections for stars unlikely to be cluster members based on their
positions in the CMD. For this data the formal Poisson uncertainties
are typically exceedingly small.  The dominant source of uncertainty
comes from the photometric calibration and from uncertainties in
cluster membership.

Near-Infrared photometry is available from \citet{cohen07}, who fit
King profiles \citet{king65} to 2MASS data in the $J$, $H$, and $K_s$
bands.  To produce NIR photometry consistent with the optical we
integrated the King profiles to the half-light radii used by
\citet{vanderbeke14}.

@@

\subsection{Star Cluster Model}
\label{sec:cluster_model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by a vector
\begin{eqnarray} \label{eq:StarModel}\displaystyle
f_{\theta_s}(\lambda_o) & = &
L(\sigma_s, z) ,\, \frac{m_*}{4\pi d_L^2(1+z)} \, s(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta_s & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \sigma_*, \beta \right]
\quad ,
\end{eqnarray} where the
parameters $\theta_s$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$, 
luminosity distance $d_L$,
and redshift $z$.
Multiplication by the matrix $L(\sigma_s, z)$ represents a convolution
with the stellar velocity profile,
and $\sigma_s$ is the stellar velocity dispersion. 
The shape of the dust attenuation curve is given by $k_\lambda \equiv
\tau_\lambda/\tau_V$.  
The observed frame wavelengths $\lambda_o$ are related to the
restframe wavelengths $\lambda$ in the usual way.

@@

The model spectra $f_{\theta_s}$ are smoothed by convolution with
the line-spread function of the spectrograph and are interpolated to
the wavelength points of the of the observed spectrum while taking
into account the redshift. For computational simplicity we assume that
the internal velocity dispersion of the cluster is negligible compared
to the instrumental broadening, though in principle it can and should
also be modeled. The instrumental resolution is given by the parameter
$\sigma_{inst}$.

@@

\item Real calibrated spectrum:   \sout{Inference using spectroscopy and all
  photometry, with full calibration model.} The calibration vector
  inferred will highlight differences between the calibrated spectrum
  and the model (which could either be due to calibration problems or
  model problems)

\item Real uncalibrated spectrum:   Inference using spectroscopy and all
  photometry, with full calibration model.

@@

In this section we describe the results of our experiments with mock
data and with real data.  For the mock data we investigate the
dependence of the recovered parameters on the type of data used in the
inference.

@@

The posterior parameter PDFs for the case of perfectly known
calibration are shown in the bottom right panels of Figure
\ref{fig:speconly_ideal}, along with the mock spectrum and posterior
samples of the mock spectrum.  In this case the observed spectrum is
the same as the intrinsic spectrum except for a distance dimming
factor, as we have assumed that the calibration vector is one
everywhere, wth no uncertainty. The PDF for stellar mass is extremely
narrow is information about the overall normalization comes from all
$\sim 3000$ spectral data points.  The single photometric data point,
with S/N of 10, adds essentially no information beyond what is
obtained from the spectrum.

Next we will \emph{not} assume that the calibration is perfectly known
and we will therefore allow the calibration parameters $\alpha$ in our
model to vary.  {\color{red} This is not converged.} In Figure
\ref{fig:speconly_calibrated} we show the result of our inference from
the spectrum and a single photometric measurement (SDSS $g$) for a
perfectly calibrated mock spectrum. To demonstrate the quality of the
fit we show both the mock input spectrum and predictions of the
observed spectra that result from several draws of the model
parameters $[\theta, \alpha]$ from posterior distribution.  We also
show samples of the inferred calibration vector,
\begin{eqnarray} \label{eq:calibration}
\frac{d}{\mu(\theta)} & = & e^{f(\alpha) + \tilde{\Delta}}
\quad ,
\end{eqnarray}
where $\tilde{\Delta}$ is the Gaussian Process mean prediction for the
logarithmic residual between the data and the model \citep{RW}.  For the
perfectly calibrated spectrum the true calibration vector (shown in
black) is one everywhere.  The spread of the inferred calibration
vectors approximately indicates our uncertainty in the spectrophotometric
calibration when no additional calibration information is available
and only a single photometric point is available.

When the spectrophotometric calibration is assumed to be unknown,
the posterior PDFs for stellar mass and especially $A_v$ become
extremely large.  There is now no information about the overall shape
of the SED (and hence the dust attenuation), and the overall
normalization is constrained entirely by the single photometric point.
The uncertainty in the stellar mass is somewhat broader than the
uncertainty on the $g$-band flux because of the variation in
mass-to-light ratio due to uncertainties in dust and, to a lesser
extent, age.

On the other hand, age and metallicity remain well-constrained.  These
are the parameters that are constrained well by spectral lines and are
not strongly sensitive to the overall shape of the spectral continuum.
The posterior PDFs are only slightly broader than in the case of a
perfectly known calibration. Such parameters can be reasonably well
recovered by fitting continuum normalized spectra, though here we have
propogated the uncertainty in this normalization into the
uncertainties on the physical parameters, leading to slightly larger
total uncertainties.

In Figure \ref{fig:speconly_uncalibrated} we show the results of
inference on an \emph{uncalibrated} mock spectrum. {\color{red} This
  is not converged}
